Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2018-03-29 revised_prop_letter_ajhs.tex
revised_prop_letter_ajhs.tex \subsection{Ultramodular Functions} Fix a typo...

The relation between ``achieving computable theory''
and ``finite precision measurement'' is more vague, but ``finite precision
measurement'' might be one of the reasons why analog computers could not be as
power as the theoratical prediction\ldots

>>>>

The relation between ``achieving computable theory''
and ``finite precision measurement'' is more vague, but ``finite precision
measurement'' might be one of the reasons why analog computers could not be as
power as the theoretical prediction\ldots
